---
title: "Goodness-of-fit test "
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}

---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(geomtextpath)
library(latex2exp)
library(univariateML)
library(viridis)
#install.packages('univariateML')
#univariateML::univariateML_models

library(fitdistrplus)
library(logspline)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)



source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")# 
source("../imagematrix.R")
#source("../imagematrix.R")
set.seed(1234567890, kind = "Mersenne-Twister")

```



The p-values of a Kolmogorov-Smirnov-Test (KS-Test) with estimated parameters can be quite wrong because the p-value does not take the uncertainty of the estimation into account. So unfortunately, you can't just fit a distribution and then use the estimated parameters in a Kolmogorov-Smirnov-Test to test your sample. There is a normality test called Lilliefors test which is a modified version of the KS-Test that allows for estimated parameters.

save(difference_values, x, file = "./Data/results_Lake_512_9W_AO_100b_36L.Rdata")
save(difference_values, x, file = "./Data/results_Lake_without_bootstrap.Rdata")
save(difference_values, x, file = "./Data/results_Lake_without_bootstrap1.Rdata")
load("./Data/results_mexico_600_9W_AO_100b_6L.Rdata")
```{r Plot_chicago_lake, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
#load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
#save(p_values_matrix, z_scores_matrix, file = "./Data/results_pvalue_Flevoland_300_7_v6.Rdata")
load("../Programs/Data/results_Phantom_4_renyi_B200_w9_08_L5.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```

```{r Plot_ottawa_AO_300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
load("../Programs/Data/results_pvalue_epsilon.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(p_values_matrix)

ggplot() +
  geom_density(aes(x = as.vector(epsilon_matrix)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```

```{r normal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
load("../Programs/Data/results_pvalue_epsilon.Rdata")
x1<-as.vector(epsilon_matrix)
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
descdist(x1, discrete = FALSE)

#fit.weibull <- fitdist(x1, "weibull")
#plot(fit.weibull)
#fit.weibull$aic
 fit.norm <- fitdist(x1, "norm")
 fit.norm$aic
 plot(fit.norm)
```

```{r Plot_ottawa_AO_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_AO_100b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```

```{r Plot_ottawa_ebra_50, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```
```{r Plot_ottawa_ebra_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```


```{r PlotAO, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_7_AO.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```


```{r PlotAO_chicago_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```

```{r PlotAO_panama_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_Mexico_512_7_AO_300b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```

```{r, eval=FALSE}
load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
#load("../Programs/Data/results_data_agua_300_7_AO.Rdata")

x2<-as.vector(difference_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```


```{r Plot_EBra, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_E.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_300b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```
```{r Plot_EBra300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r Plot_EBra1b, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_1b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```


```{r Plot_correa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_9_correa.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r, eval=FALSE}
#load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")

x2<-as.vector(difference_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```


```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
x1<-as.vector(difference_values)

descdist(x1, discrete = FALSE)

#fit.weibull <- fitdist(x1, "weibull")
#plot(fit.weibull)
#fit.weibull$aic
 fit.norm <- fitdist(x1, "norm")
 fit.norm$aic
 plot(fit.norm)
```


```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
x1<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x1)
mydata_dist
```

```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
alpha <- 5.452
beta <- 2.061


pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}


p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    
    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}


save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix ))
#plot(imagematrix(p_values_matrix >0.1))
```

```{r cv_lognormal, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
plnorm_inv <- function(x, meanlog, sdlog) {
  pnorm(log(x), mean = meanlog, sd = sdlog)
}

# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.1931404
sdlog <- 0.4293747

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    # Calcular el p-valor utilizando la función de distribución acumulativa inversa de la distribución lognormal
    p_values_matrix[i, j] <- plnorm_inv(cv_value, meanlog, sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cv_values)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.1))
```

```{r cv_lognormal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
load("../Programs/Data/results_data_simulated_Phantom_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# Cargar los datos y parámetros de ajuste de la distribución lognormal
# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.1503808
sdlog <-  0.4504363

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    # Calcular el p-valor utilizando la función plnorm()
    p_values_matrix[i, j] <- 1-plnorm(cv_value, meanlog = meanlog, sdlog = sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cv_values)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.1))
```







```{r cv_lognormal3_mnad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_simulated_z_up_le_mnad_250_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# Cargar los datos y parámetros de ajuste de la distribución lognormal
# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.2861518
sdlog <- 0.5366815

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cd_values_mnad), ncol = ncol(cd_values_mnad))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cd_values_mnad)) {
  for (j in 1:ncol(cd_values_mnad)) {
    cd_value_mnad <- cd_values_mnad[i, j]
    
    # Calcular el p-valor utilizando la función plnorm()
    p_values_matrix[i, j] <- 1-plnorm(cd_value_mnad, meanlog = meanlog, sdlog = sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.05))
```

```{r cv_lognormal3_entropy, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }

load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
# Calcular la media y la desviación estándar de los datos originales
mean_original <- mean(difference_values, na.rm = TRUE)
sd_original <- sd(difference_values, na.rm = TRUE)

# Normalizar los datos
normalized_data <- (difference_values - mean_original) / sd_original

# Parámetros de la distribución normal estándar
mean_standard <- 0
sd_standard <- 1

# Definir función para calcular los p-valores
calculate_p_value <- function(x) {
  p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
  return(p_value)
}

# Dimensiones de la matriz difference_values
n_rows <- nrow(normalized_data)
n_cols <- ncol(normalized_data)

# Matriz para almacenar los p-valores
p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)

# Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
for (i in 1:n_rows) {
  for (j in 1:n_cols) {
    p_values[i, j] <- calculate_p_value(normalized_data[i, j])
  }
}

# Guardar los p-valores
#save(p_values, file = "p_values_matrix_normalized.Rdata")


#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
#save(p_values, file = "../Programs/Data/p_values_matrix_normalized.Rdata")
#load("../Programs/Data/p_values_matrix_normalized.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# # Cargar los datos y parámetros de ajuste de la distribución lognormal
# # Cargar los datos y parámetros de ajuste de la distribución lognormal
# # Calcular la media y la desviación estándar de los datos originales
# mean_original <- mean(difference_values, na.rm = TRUE)
# sd_original <- sd(difference_values, na.rm = TRUE)
# 
# # Normalizar los datos
# normalized_data <- (difference_values - mean_original) / sd_original
# 
# # Parámetros de la distribución normal estándar
# mean_standard <- 0
# sd_standard <- 1
# 
# # Definir función para calcular los p-valores
# calculate_p_value <- function(x) {
#   p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
#   return(p_value)
# }
# 
# # Dimensiones de la matriz difference_values
# n_rows <- nrow(normalized_data)
# n_cols <- ncol(normalized_data)
# 
# # Matriz para almacenar los p-valores
# p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)
# 
# # Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
# for (i in 1:n_rows) {
#   for (j in 1:n_cols) {
#     p_values[i, j] <- calculate_p_value(normalized_data[i, j])
#   }
# }
# 
# # Guardar los p-valores
# save(p_values, file = "../Programs/Data/p_values_matrix_normalized_1.Rdata")

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
#plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
plot(imagematrix(p_values ))
plot(imagematrix(p_values <0.1))
plot(imagematrix(p_values >0.5))
```

```{r Plot2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 7x7, Flevoland" }

load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "blue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
source("../imagematrix.R")
#hist(cv_values)
```



```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```
```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland", eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
alpha <- 5.762
beta <- 2.611


pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}


p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    
    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}


#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
valores_menores_que_0_05 <- sum(p_values_matrix < 0.05)
cat("Número de valores menores que 0.05:", valores_menores_que_0_05, "\n")

```



```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```


```{r cv9, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 9x9, Flevoland"}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
alpha <- 3.58
beta <- 1.32


pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}


p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    
    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}


#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.1))
```

```{r Plot3, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "red", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```



```{r 5ottawa, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```


```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
alpha <- 5.29
beta <- 2.20 


pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}


p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    
    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}


#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


source("../imagematrix.R")
hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
```

```{r Plotcqv, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "green", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```


```{r 5ottawa_cqv, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```



```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
alpha <- 3.58
beta <- 1.32


pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}


p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]
    
    
    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}


#save(x, p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")


source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
#plot(imagematrix(p_values_matrix <0.05))
```



```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cd_values_mad)), fill = "pink", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 5ottawa_mad, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")
x2<-as.vector(cd_values_mad)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_7.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cd_values_mad)), fill = "blue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

<!-- ```{r} -->
<!-- load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata") -->
<!-- x1<-as.vector(cv_values) -->
<!-- n.sims <- 100 -->

<!-- stats <- replicate(n.sims, { -->
<!--   r <- rweibull(n = length(x1) -->
<!--                 , shape= fit.weibull$estimate["shape"] -->
<!--                 , scale = fit.weibull$estimate["scale"] -->
<!--   ) -->
<!--   estfit.weibull <- fitdist(r, "weibull") # added to account for the estimated parameters -->
<!--   as.numeric(ks.test(r -->
<!--                      , "pweibull" -->
<!--                      , shape= estfit.weibull$estimate["shape"] -->
<!--                      , scale = estfit.weibull$estimate["scale"])$statistic -->
<!--   ) -->
<!-- }) -->

<!-- plot(ecdf(stats), las = 1, main = "KS-test statistic simulation (CDF)", col = "darkorange", lwd = 1.7) -->
<!-- grid() -->


<!-- ``` -->
